\newpage
\section{Conditions}
\label{conditions}
This section lists the conditions a unit can potentially have. The race-specific conditions are either only applicable to or caused by units from that race.

\subsection{Workers}
\begin{tabularx}{\textwidth}{lX}
 \verb|carrying| & Indicates when a worker unit is carrying minerals or vespene gas. \\
 \verb|constructing| & Shows that a worker unit is busy constructing a building. \\
 \verb|gathering| & Show that a worker unit is busy gathering minerals or vespene gas. \\
 \verb|repairing| & Shows that a (Terran) worker unit is busy repairing a building.
\end{tabularx}

\subsection{Generic}
\begin{tabularx}{\textwidth}{lX}
 \verb|attacking| & Indicates when a unit is attacking an other unit (includes medic heal). \\
 \verb|beingConstructed| & Indicates that a unit is incomplete (includes morphing). \\
 \verb|cloaked| & Indicates that a unit is cloaked. \\
 \verb|coolingDown| & Indicates that a unit cannot attack due to cooldown. \\
 \verb|detected| & Indicates that an enemy cloaked/burrowed unit has been detected (and thus can be attacked). \\
 \verb|flying| & Indicates that a unit is flying. \\
 \verb|following| & Indicates that a unit is following an other unit. \\
 \verb|holding| & Indicates that a unit is holding a position. \\
 \verb|idle| & Indicates that the unit is idle (not doing anything). \\
 \verb|loaded| & Indicates that a unit is loaded (i.e. has one or more units in it). \\
 \verb|moving| & Indicates that a unit is moving. \\
 \verb|patrolling| & Indicates that a unit is patrolling between 2 positions. \\
 \verb|underAttack| & Indicates that a unit is under attack.
\end{tabularx}

\subsection{Zerg}
\begin{tabularx}{\textwidth}{lX}
 \verb|acidSpored | & Indicates that a unit is under Acid Spores from a Defiler. \\
 \verb|burrowed| & Indicates that a unit is burrowed. \\
 \verb|darkSwarmed| & Indicates that a unit is under a Dark Swarm from a Defiler. \\
 \verb|ensnared| & Indicates that a unit is ensnared by a Queen. \\
 \verb|morphing| & Indicates that a unit is morphing. \\
 \verb|parasited| & Indicates that a unit is parasited by a Queen. \\
 \verb|plagued| & Indicates that a unit is plagued by a Defiler.
\end{tabularx}

\subsection{Terran}
\begin{tabularx}{\textwidth}{lX}
 \verb|<addonName>| & Indicates that an addon of a building is present. \\
 \verb|beingHealed| & Indicates that a unit is being healed by a Medic or repaired by a SCV. \\
 \verb|blinded| & Indicates that a unit is blinded by a Medic. \\
 \verb|defenseMatrixed| & Indicates that a unit has a defensive matrix on it (from a Science Vessel).\\
 \verb|hasMines| & Indicates that a Vulture has at least one Spider Mine. \\
 \verb|irradiated| & Indicates that a unit is irradiated by a Science Vessel. \\
 \verb|lifted| & Indicates that a building is lifted (and thus can move). \\
 \verb|lockDowned| & Indicates that a unit is under lockdown by Ghost. \\
 \verb|nukeReady| & Indicates that a Nuclear Silo is ready to launch a Nuclear Missile. \\
 \verb|sieged| & Indicates that a Siegetank is in siegemode. \\
 \verb|stimmed| & Indicates that a Firebat or Marine is stimmed.
\end{tabularx}

\subsection{Protoss}
\begin{tabularx}{\textwidth}{lX}
 \verb|disruptionWebbed| & Indicates that a unit is in a disruption web from a Corsair. \\
 \verb|hallucination| & Indicates that a friendly unit is a hallucination (from a High Templar) \\
  \verb|hasInterceptors| & Indicates that a Carrier has at least one Interceptor. \\
 \verb|hasScarabs| & Indicates that a Reaver has at least one Scarab. \\
 \verb|maelstrommed| & Indicates that a unit is maelstrommed by a Dark Archon. \\
 \verb|stasised| & Indicates that a unit is stuck in stasis from an Arbiter. \\
 \verb|underStorm| & Indicates that a unit is under a storm from a High Templar. \\
 \verb|unpowered| & Indicates that a building is no longer powered by a pylon (e.g. a Photon Cannon then no longer functions).
\end{tabularx}