\newpage
\section{Abilities}
\label{abilities}
All abilities that can be used by the indicated units of each race, usually after having the researched the corresponding upgrade (exceptions to this are noted). The potential target(s) is/are indicated in brackets.

\subsection{Terran}

\paragraph{Battle Cruiser} \mbox{}\\
\verb|Yamato Gun| (\textit{unit}) \\

\paragraph{Comsat Station} \mbox{}\\
\verb|Scanner Sweep| (\textit{position or unit}) \\

\paragraph{Ghost} \mbox{}\\
\verb|Lockdown| (\textit{unit}) \\
\verb|Personnel Cloaking| (\textit{self}) \\
\verb|Nuclear Strike| (\textit{position or unit})

\paragraph{Marine / Firebat} \mbox{}\\
\verb|Stim Packs| (\textit{self})

\paragraph{Medic} \mbox{}\\
\verb|Healing| (\textit{position or unit}) \\
\verb|Restoration| (\textit{unit}) \\
\verb|Optical Flare| (\textit{unit})

\paragraph{Science Vessel} \mbox{}\\
\verb|Defensive Matrix| (\textit{unit}) \\
\verb|EMP Shockwave| (\textit{position or unit}) \\
\verb|Irradiate| (\textit{unit})

\paragraph{Siege Tank} \mbox{}\\
\verb|Tank Siege Mode| (\textit{self})

\paragraph{Vulture} \mbox{}\\
\verb|Spider Mines| (\textit{position})

\paragraph{Wraith} \mbox{}\\
\verb|Cloaking Field| (\textit{self})

\subsection{Protoss}

\paragraph{Arbiter} \mbox{}\\
\verb|Recall| (\textit{position or unit}) \\
\verb|Stasis Field| (\textit{position or unit})

\paragraph{Corsair} \mbox{}\\
\verb|Disruption Web| (\textit{position or unit})

\paragraph{Dark Archon} \mbox{}\\
\verb|Feedback| (\textit{unit}) \\
\verb|Maelstrom| (\textit{position or unit}) \\
\verb|Mind Control| (\textit{unit})

\paragraph{Dark Templar} \mbox{}\\
\verb|Dark Archon Meld| (\textit{unit})

\paragraph{High Templar} \mbox{}\\
\verb|Archon Warp| (\textit{unit}) \\
\verb|Psionic Storm| (\textit{position or unit}) \\
\verb|Hallucination| (\textit{unit})

\subsection{Zerg}

\paragraph{Generic} \mbox{}\\
\verb|Burrowing| (\textit{self}) \\
\textit{Lurkers can use this ability without having it researched; for Zerglings, Defilers, Hydralisks and Drones the upgrade needs to be researched.}

\paragraph{Defiler} \mbox{}\\
\verb|Dark Swarm| (\textit{position or unit}) \\
\verb|Plague| (\textit{position or unit}) \\
\verb|Consume| (\textit{unit}) 

\paragraph{Queen} \mbox{}\\
\verb|Infestation| (\textit{unit}) \\
\verb|Parasite| (\textit{unit}) \\
\verb|Ensnare| (\textit{position or unit}) \\
\verb|Spawn Broodlings| (\textit{unit})

\section{Known Limitations}
Here we list functionalities that the connector does not support at this time:
\begin{itemize}
 \item Getting more detailed information about the map like the exact shapes of regions and non-walkable locations.
 \item Detecting `bullets' like Psionic Storms and Subterranean Spikes.
 \item Detecting upgrades performed by the enemy player.
 \item Specifying the random seed used for a match.
 \item Automatically pausing the game when a whole MAS is paused.
\end{itemize}